\documentclass[xcolor=dvipsnames,notes]{beamer}
\usecolortheme[named=Brown]{structure}
\usetheme{default}
\setbeamertemplate{navigation symbols}{} 
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
\usetikzlibrary{datavisualization.formats.functions}
\include{macro}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{multimedia}
\begin{document}
%\setbeamercolor{titlelike}{fg=gray,bg=white}
%\setbeamercolor{itemize item}{fg=gray,bg=white}
%\setbeamercolor{enumerate item}{fg=gray,bg=white}
%\setbeamercolor{block title}{fg=black,bg=white}
%==============================================
\title{TPG4190 Seismic data acquisition and processing}
\author{B. Arntsen}
\institute[NTNU]{
  NTNU\\
  Department of Geoscience and petroleum \\
  \texttt{borge.arntsen@ntnu.no}
}
\date{Trondheim fall 2022}
\begin{frame}
 \titlepage
\end{frame}
%==============================================
%-----------------------------------------
\begin{frame}{Curriculum}
%-----------------------------------------
\begin{enumerate}
  \item Martin Landr\o Lecture notes Sections 2.2-2.10
  \item Lecture 1: Sources 
  \item Lecture 2: Receivers
  \item Lecture 3: The CMP method
  \item Lecture 4: Fourier transforms
  \item Lecture 5: Deghosting
  \item Lecture 6: Seismic modelling 
  \item Lecture 8: Filters
  \item Lecture 9: Processing
  \item Lecture 12: Reverse-Time Migration (RTM)
  \item Lecture 15: Ray modelling
  \item Lecture 17: Radon demult
  \item Lecture 18: Surface Related Multiple Removal (SRME)
  \item Lecture 19: Tomography
  \item Lecture 21: Full Waveform Inversion (FWI)
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Sources}
%-----------------------------------------
\begin{enumerate}
  \item What is an airgun
  \item Bubble
  \item P/B ratio
  \item Ghost
  \item Ghost spectrum - depth relation
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Receivers}
%-----------------------------------------
\begin{enumerate}
  \item Array response of receiver groups
  \item Anti-Aliasing
\end{enumerate}
\end{frame}
%\end{frame}
%-----------------------------------------
\begin{frame}{CMP method}
%-----------------------------------------
\begin{enumerate}
  \item CMP sorting
  \item Fold
  \item 2D - 3D  Flip-Flop sources
  \item NMO - Stack
  \item RMS velocity
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Fourier transforms}
%-----------------------------------------
\begin{enumerate}
  \item What is a Fourier transform
  \item Simple Fourier transforms
  \item Nyquist limit, sampling, Aliasing
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Deghosting}
%-----------------------------------------
\begin{enumerate}
  \item Up-Down separation  
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Seismic modelling}
%-----------------------------------------
\begin{enumerate}
  \item What is it?
  \item What is it used for?
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Filters}
%-----------------------------------------
\begin{enumerate}
  \item Convolution in the Fourier domain
  \item impulse response
  \item Common filters and
        what are they used for
  \item F-K filters
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Processing}
%-----------------------------------------
\begin{enumerate}
  \item Basic processing sequence
  \item Principle for migration (imaging)
  \item Kirchhoff migration
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Reverse time migration}
%-----------------------------------------
\begin{enumerate}
  \item What is RTM 
  \item Cost/Benefit
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Ray modelling}
%-----------------------------------------
\begin{enumerate}
  \item What are rays?
  \item How is Ray modelling used?
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Radon transform}
%-----------------------------------------
\begin{enumerate}
  \item What is the Radon transform
  \item How is the Radon transform used for 
        removing multiples?
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{SRME}
%-----------------------------------------
\begin{enumerate}
  \item What is the basic idea behind SRME?
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{Tomography}
%-----------------------------------------
\begin{enumerate}
  \item What is tomography
\end{enumerate}
\end{frame}
%-----------------------------------------
\begin{frame}{FWI}
%-----------------------------------------
\begin{enumerate}
  \item What is Full Waveform Inversion? 
  \item What is FWI used for?
\end{enumerate}
\end{frame}
\end{document}

